---
title: "Robust RM Anova"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(ez)
library(nlme)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS)
library(reshape)
```
```{r}
df<- read.delim('/home/atrides/Desktop/R/statistics_with_R/13_GLM4_RepeatedMeasuresDesigns/Data_Files/Bushtucker.dat', header = TRUE)
```
## we will use the package WRS, which needs the data in wide format 

## we will use functions as rmanova(), rmmcp() , rmanovab(), pairdepb()
```{r}
df<- df[, -c(1)]
```
### one way repeated measure anova based on trimmed means, rmanova(data, tr = .2)
```{r}
rmanova(df)
```

### performs one-way repeated-measures ANOVA using a bootstrap procedure, rmanovab(data, tr = .2, alpha = .05, nboot = 599)
```{r}
rmanovab(df, nboot=2000)
```

### performs post hoc tests for one-way repeated-measures design based on trimmed means.
```{r}
rmmcp(df)
```

### performs post hoc test according to rmanovab()
```{r}
pairdepb(df, nboot = 2000)
```

# Conclusion: According to all robust anova and post-hoc tests , none of groups differ significantly


